---
title: "Class06-Part.1"
author: "Maria Koh"
date: "Saturday, September 20, 2014"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
    latex_engine: xelatex
---
This is the project for the statistical inference class. 
The exponential distribution can be simulated in R with rexp(nosim, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. 
Set lambda = 0. 2 for all of the simulations.

1. Show where the distribution is centered at and compare it to the theoretical center of the distribution. 
```{r}
   library(knitr)
	 library(ggplot2)

   nn <- 40
	 lambda <- 0.2
	 mean_data <- 1/lambda
	 sd_data <- 1/lambda*1/sqrt(nn)
```
I repeated the simulation for 1000 times.
I make the plot using ggplot for Sample and normal distribution using line.
```{r}
   nosim <- 1000
	 reap_matrix <- matrix( rexp(nosim*nn , rate=lambda), nosim)
	 rexp_mean <- apply(reap_matrix, 1, mean)
	 rexp_sd <- apply(reap_matrix, 1, sd)
   rexp_df <- data.frame(dfmean=rexp_mean, dfsd=rexp_sd)
```
Show the plot
```{r}
 ggplot(rexp_df, aes(x = dfmean)) +
 geom_bar(binwidth = 0.1, aes(y = ..density.. ), fill = "#99FF99",  colour ="#999999" , position = "identity" ) +
 stat_function( fun = dnorm, colour = "#009E73", arg = list (mean = mean_data, sd = sd_data))+
 ggtitle("Sampling data with normal distribution curve")
```
that is the  mean for sample and theoretical mean.
```{r}
  sample_mean <- mean(rexp_mean)
 	theoretical_mean <- 1/ lambda
 	print(paste("sample_mean =", sample_mean))
 	print(paste("theoretical_mean =", mean_data))
```
2. Show how variable it is and compare it to the theoretical variance of the distribution. 
```{r}
  sample_sd <- sd(rexp_mean)
	print(sample_sd)

	theoretical_sd <- 1/lambda * 1/sqrt(nn)
	print(theoretical_sd)
```
3. Show that the distribution is approximately normal using more repetition.
```{r}
  nosim2 <- 100000
  reap_matrix2 <- matrix( rexp(nosim2*nn , rate=lambda), nosim2)
	rexp_mean2 <- apply(reap_matrix2, 1, mean)
	rexp_sd2 <- apply(reap_matrix2, 1, sd)
  rexp_df2 <- data.frame(dfmean=rexp_mean2, dfsd=rexp_sd2)
```
I repeated the simulation for 100000 times.
```{r}
ggplot(rexp_df2, aes(x = dfmean)) +
 geom_bar(binwidth = 0.1, aes(y = ..density..), fill = "#FFFF99", colour ="#999999" , position = "identity" ) +
 stat_function( fun = dnorm, colour = "#009E73", arg = list (mean = mean_data, sd = sd_data))+
 ggtitle("Sampling data with normal distribution curve")

```
4. Evaluate the coverage of the confidence interval for 1/lambda : X ±1. 96 * S * 1/sqrt(n). 
```{r}
 large_sample_mean <- mean(rexp_mean2)
 large_sample_sd <- sd(rexp_mean2)
 
 sample_interval <- sample_mean+ c(-1, 1) * 1.96 * sample_sd * 1/sqrt(nn)
 large_sample_interval <- large_sample_mean+ c(-1, 1) * 1.96 * large_sample_sd * 1/sqrt(nn)

 theory_interval <- mean_data + c(-1, 1) * 1.96 * 1/lambda * 1/sqrt(nn)
 
 print(paste("theoretical_mean =", mean_data))
 print(paste("Sample's Interval",sample_interval)) 
 print(paste("Large Sample's Interval",large_sample_interval)) 
 print(paste("Theory's Interval",theory_interval)) 

```
