---
title: "Class06-PartII"
author: "Maria Koh"
date: "Saturday, September 20, 2014"
output:
  pdf_document:
    fig_crop: no
    fig_height: 3
    keep_tex: yes
---
This is the project Part 2 for the statistical inference class. 
1.Load the ToothGrowth data and perform some basic exploratory data analyses 
```{r}
 library(knitr)
 library(ggplot2)
 library(plyr)
 data(ToothGrowth)
```
perform some basic exploratory data analyses using means for length by supp and dose
```{r}
ToothGrowth.OJ <- subset(ToothGrowth, ToothGrowth$supp == "OJ")
ToothGrowth.VC <- subset(ToothGrowth, ToothGrowth$supp == "VC")  

res.OJ <- data.frame( res.dose=unique(ToothGrowth.OJ$dose), res.mean=tapply(ToothGrowth.OJ$len, ToothGrowth.OJ$dose, mean) , res.supp="OJ")
res.VC <- data.frame( res.dose=unique(ToothGrowth.VC$dose), res.mean=tapply(ToothGrowth.VC$len, ToothGrowth.VC$dose, mean) , res.supp="VC")
res <- merge( res.OJ , res.VC, all = TRUE)
```
I embed plots for  ToothGrowth.
```{r}
ggplot( data=res) +
geom_bar(aes(x=as.numeric(res$res.dose), y=res$res.mean, fill=res$res.supp), stat="identity", position="dodge") +
labs(fill="supp") + ggtitle("ToothGrowth by supp") + ylab("Mean by supp") + xlab("dose")
```
2.Provide a basic summary of the data.
```{r}
summary( ToothGrowth)

ToothGrowth$dose = factor(ToothGrowth$dose, levels=c( 0.5, 1.0, 2.0), labels = c("low", "med", "high"))
boxplot(len ~supp*dose, data=ToothGrowth, ylab="Tooth Length", main = "boxplots")
```
3.Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose.(Use the techniques from class even if there's other approaches worth considering)

3-1) Compare Orange Juice vs. Ascorbic Acid ignored dose type. 
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ"],ToothGrowth$len[ToothGrowth$supp=="VC"])
```
  H0 - There aren't significant differences in the impact of the Orange Juice and Ascorbic  Acid.So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(0.06063) is larger than the 0.05, Ho accepted, There aren't the significant differences in the impact of the Orange Juice and Ascorbic Acid

3-2) Compare Orange Juice vs. Ascorbic Acid for only low(0.5mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="low"],ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="low"])
```
  H0 - There aren't significant differences in the impact of the Orange Juice and Ascorbic Acid for low(0.5 mg)  dose.So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(0.006359) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the Orange Juice and Ascorbic Acid for low dose.

3-3) Compare Orange Juice vs. Ascorbic Acid for only med(1mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="med"],ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="med"])
```
  H0 - There aren't significant differences in the impact of the Orange Juice and Ascorbic Acid for medium(1 mg) dose.So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(0.001038) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the Orange Juice and Ascorbic Acid for low dose.

3-4) Compare Orange Juice vs. Ascorbic Acid for only high(2mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="high"],ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="high"])
```
  H0 - There aren't significant differences in the impact of the Orange Juice and Ascorbic Acid for High(2 mg) dose.So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(0.9639) is larger than the 0.05, Ho accepted, There aren't the significant differences in the impact of the Orange Juice and Ascorbic Acid for high dose.

3-5) For Orange Juice, Compare low(0.5mg) dose type vs. med(1mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="low"],ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="med"])
```
  H0 - There aren't significant differences in the impact for the Low(0.5mg) dose and Medium(1 mg) dose in the Orange Juice. So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(8.785e-05) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the dose.

3-6) For Orange Juice, Compare low(0.5mg) dose type vs. high(2mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="low"],ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="high"])
```
  H0 - There aren't significant differences in the impact for the Low(0.5mg) dose and Medium(1 mg) dose in the Orange Juice. So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(1.324e-06) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the dose.

3-7) For Orange Juice, Compare med(1mg) dose type vs. high(2mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="med"],ToothGrowth$len[ToothGrowth$supp=="OJ"&ToothGrowth$dose=="high"])
```
  H0 - There aren't significant differences in the impact for the Low(0.5mg) dose and Medium(1 mg) dose in the Orange Juice. So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(0.0392) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the dose.

3-8) For Ascorbic Acid, Compare low(0.5mg) dose type vs. med(1mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="low"],ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="med"])
```
  H0 - There aren't significant differences in the impact for the Low(0.5mg) dose and Medium(1 mg) dose in the Ascorbic Acid. So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(6.811e-07) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the dose.

3-9) For Ascorbic Acid, Compare low(0.5mg) dose type vs. high(2mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="low"],ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="high"])
```
  H0 - There aren't significant differences in the impact for the Low(0.5mg) dose and high(2 mg) dose in the Ascorbic Acid. So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(4.682e-08) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the dose.

3-10) For Ascorbic Acid, Compare med(1mg) dose type vs. high(2mg) dose type.
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="med"],ToothGrowth$len[ToothGrowth$supp=="VC"&ToothGrowth$dose=="high"])
```
  H0 - There aren't significant differences in the impact for the Medium(1mg) dose and High(2 mg) dose in the Ascorbic Acid. So, The differences of  two group's means are 0. 
  As the result the t test, 
  p-value(9.156e-05) is less than the 0.05, Ho rejected, There are the significant differences in the impact of the dose.

4.State your conclusions and the assumptions needed for your conclusions.

There aren't the significant differences in the impact of the Orange Juice and Ascorbic Acid
But, There are the significant differences in the impact for their dose.
